The problem and promise of scale in multilayer animal social networks

### 2020-02-15 paper/manuscript.Rmd
middle conclusion para

<!-- 
TODO: Schneider 2001, Levin og,

Alec, I think you need to include a paragraph reflecting on the importance of scale and ~3 critical things we should take away from this (maybe especially in light of including spatial data?) -->

Multilayer networks are complicated in that they can incorporate data as varied
as social interactions, landscape features, and seasons, all of which exist at
different scales and units of measurement. Our analysis of caribou multilayer
networks incorporated high resolution GPS telemetry data and spatial landcover
data is grounded in the context of observed animal social networks, as the
scales we chose to explore, e.g., number of observations, sociality across space
and time, are ones that can be observed as has traditionally been done in
ethology. Thus, we highlight ways in which scale ought to be considered for both
observed and remotely-sensed data when building social networks. Furthermore,
GPS telemetry data provides a link between large scale landscape properties and
fine scale social interactions as animal movement occurs across the landscape,
and when taken into account with multiple individuals can indicate association
patterns. Thus, a layer incorporating relocation data could be a great boon
linking spatial and social layer in multilayer networks.

>>>>

Recognition of scale as a fundamental concept in ecology [@Levin_1992] has lead
to an increased attention to the scale at which ecological processes are
observed [@Schneider_2001; @Chave_2013]. In addition, recent technological
advances have lead to increased data complexity and resolution. Remotely sensed
imagery collected by modern satellites provide, for example, 10 m spatial
resolution optical imagery at a temporal revisit period of five days at the
equator [@Drusch_2012]. Similarly, animal tracking devices have become smaller
allowing their deployement on a wider variety of organisms [@Wikelski_2007] and
at a higher temporal resolution [@Börger_2016]. Given this increased
availability of complex data, it is important to consider using a broad
continuum of scales to fully capture ecological processes, carefully select and
combine sources of data with different temporal and spatial scales, and
establish a clear link between scales of observation and meaningful biology.

Multilayer networks are complicated in that they can incorporate data as varied
as social interactions, landscape features, and seasons, all of which exist at
different scales and units of measurement. Our analysis of caribou multilayer
networks which incorporated high resolution GPS telemetry data and spatial landcover
data is grounded in the context of observed animal social networks, as the
scales we chose to explore, e.g., number of observations, sociality across space
and time, are ones that can be observed as has traditionally been done in
ethology. We highlight ways in which scale ought to be considered for both
observed and remotely-sensed data when building social networks. Furthermore,
GPS telemetry data provides a link between large scale landscape properties and
fine scale social interactions as animal movement occurs across the landscape,
and when taken into account with multiple individuals can indicate association
patterns. Thus, a layer incorporating relocation data could be a great boon
linking spatial and social layer in multilayer networks.
